CF Registry Analysis - ROC

### 2025-09-16 Christine Chan/CF Registry/cf_registry_ROC_analysis.qmd
updates for Monique

```{r setup}
#| include: false
library(dplyr)
library(tidyr)
library(ggplot2)
library(gtsummary)
library(gt)
library(pROC)
library(ggrepel)
home_dir <- switch(Sys.info()["sysname"],
    "Darwin" = "/Users/tim/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Christine Chan/CF Registry",
    "Windows" = "C:/Users/tim/OneDrive - The University of Colorado Denver/Vigers/CF/Christine Chan/CF Registry",
    "Linux" = "/home/tim/OneDrive/Vigers/CF/Christine Chan/CF Registry"
)
github_dir <- switch(Sys.info()["sysname"],
    "Darwin" = "/Users/timvigers/GitHub",
    "Windows" = "C:/Users/Tim/GitHub",
    "Linux" = "/home/tim/GitHub"
)
knitr::opts_knit$set(root.dir = home_dir)
set.seed(1017)
```

@@

@@

@@

# Metrics to report
metrics <- c(
    "thresh",
    "specificity",
    "sensitivity",
    "accuracy",
    "tn",
    "tp",
    "fn",
    "fp",
    "npv",
    "ppv"

@@

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = ngt_agt)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = agt_cfrd)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = peds_ngt_agt)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = peds_agt_cfrd)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = adult_ngt_agt)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = adult_agt_cfrd)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = white_ngt_agt)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = white_agt_cfrd)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = black_ngt_agt)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = black_agt_cfrd)
roc_plot(r)
gt(data.frame(coords(r, "best"))) %>%
    fmt_number(n_sigfig = 3)
gt(data.frame(ci.coords(r, "best", best.policy = "random"))) %>%
    fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = more_ngt_agt)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = more_agt_cfrd)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = other_ngt_agt)
roc_plot(r)
gt(data.frame(coords(r, "best"))) %>%
    fmt_number(n_sigfig = 3)
gt(data.frame(ci.coords(r, "best", best.policy = "random"))) %>%
    fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = other_agt_cfrd)
roc_plot(r)
gt(data.frame(coords(r, "best"))) %>%
    fmt_number(n_sigfig = 3)
gt(data.frame(ci.coords(r, "best", best.policy = "random"))) %>%
    fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = hispanic_ngt_agt)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = hispanic_agt_cfrd)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = non_hispanic_ngt_agt)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = non_hispanic_agt_cfrd)
roc_plot(r)
gt(data.frame(coords(r, "best"))) %>%
    fmt_number(n_sigfig = 3)
gt(data.frame(ci.coords(r, "best", best.policy = "random"))) %>%
    fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(agt ~ hgba1c, data = roc_df)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(cfrd ~ hgba1c, data = roc_df)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(agt ~ hgba1c, data = peds_roc)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(cfrd ~ hgba1c, data = peds_roc)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(agt ~ hgba1c, data = adult_roc)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(cfrd ~ hgba1c, data = adult_roc)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(agt ~ hgba1c, data = white_roc)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(cfrd ~ hgba1c, data = white_roc)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(agt ~ hgba1c, data = black_roc)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(cfrd ~ hgba1c, data = black_roc)
roc_plot(r)
gt(data.frame(ci.coords(r, "best", best.policy = "random"))) %>%
    fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(agt ~ hgba1c, data = more_roc)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(cfrd ~ hgba1c, data = more_roc)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(agt ~ hgba1c, data = other_roc)
roc_plot(r)
gt(data.frame(coords(r, "best"))) %>%
    fmt_number(n_sigfig = 3)
gt(data.frame(ci.coords(r, "best", best.policy = "random"))) %>%
    fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(cfrd ~ hgba1c, data = other_roc)
roc_plot(r)
gt(data.frame(coords(r, "best"))) %>%
    fmt_number(n_sigfig = 3)
gt(data.frame(ci.coords(r, "best"))) %>%
    fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(agt ~ hgba1c, data = hispanic_roc)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(cfrd ~ hgba1c, hispanic_roc)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all", ret = "all"))) %>% fmt_number(n_sigfig = 3)
```

>>>>

```{r setup}
#| include: false
library(dplyr)
library(tidyr)
library(ggplot2)
library(gtsummary)
library(gt)
library(pROC)
library(ggrepel)
home_dir <- switch(
    Sys.info()["sysname"],
    "Darwin" = "/Users/tim/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Christine Chan/CF Registry",
    "Windows" = "C:/Users/tim/OneDrive - The University of Colorado Denver/Vigers/CF/Christine Chan/CF Registry",
    "Linux" = "/home/tim/OneDrive/Vigers/CF/Christine Chan/CF Registry"
)
github_dir <- switch(
    Sys.info()["sysname"],
    "Darwin" = "/Users/timvigers/GitHub",
    "Windows" = "C:/Users/Tim/GitHub",
    "Linux" = "/home/tim/GitHub"
)
knitr::opts_knit$set(root.dir = home_dir)
set.seed(1017)
```

@@

# Format CFTR modulator variables
encounter$Vx770[is.na(encounter$Vx770)] <- 0
encounter$Vx770 <- factor(
    encounter$Vx770,
    levels = 0:1,
    labels = c("No", "Yes")
encounter$Vx809comb[is.na(encounter$Vx809comb)] <- 0
encounter$Vx809comb <- factor(
    encounter$Vx809comb,
    levels = 0:1,
    labels = c("No", "Yes")

@@

    drop_na(
        hgba1c

@@

@@

### Pairwise comparisons

#### <140 vs. [140,200)

```{r}
roc_df %>%
    select(`OGTT 2-hour`, Gender, MutClass, hgba1c) %>%
    filter(`OGTT 2-hour` != ">=200") %>%
    mutate(`OGTT 2-hour` = droplevels(`OGTT 2-hour`)) %>%
    tbl_summary(
        by = `OGTT 2-hour`,
        missing_text = "Missing",
        type = list(all_continuous() ~ "continuous2"),
        statistic = list(
            all_continuous() ~
                c("{mean} ({sd})", "{median} ({p25}, {p75})", "{min}, {max}")
        ),
        label = list(
            hgba1c = "HbA1c",
            Hispanicrace = "Hispanic",
            MutClass = "Mutation Class",
            reviewyear = "Year",
            Age_YrEnd = "Age at Year End"
        )
    ) %>%
    add_overall() %>%
    add_p(
        test = list(reviewyear = "fisher.test"),
        test.args = all_tests("fisher.test") ~ list(simulate.p.value = T)
    ) %>%
    separate_p_footnotes() %>%
    as_gt()
```

#### [140,200) vs. >=200

```{r}
roc_df %>%
    select(`OGTT 2-hour`, Gender, MutClass, hgba1c) %>%
    filter(`OGTT 2-hour` != "<140") %>%
    mutate(`OGTT 2-hour` = droplevels(`OGTT 2-hour`)) %>%
    tbl_summary(
        by = `OGTT 2-hour`,
        missing_text = "Missing",
        type = list(all_continuous() ~ "continuous2"),
        statistic = list(
            all_continuous() ~
                c("{mean} ({sd})", "{median} ({p25}, {p75})", "{min}, {max}")
        ),
        label = list(
            hgba1c = "HbA1c",
            Hispanicrace = "Hispanic",
            MutClass = "Mutation Class",
            reviewyear = "Year",
            Age_YrEnd = "Age at Year End"
        )
    ) %>%
    add_overall() %>%
    add_p(
        test = list(reviewyear = "fisher.test"),
        test.args = all_tests("fisher.test") ~ list(simulate.p.value = T)
    ) %>%
    separate_p_footnotes() %>%
    as_gt()
```

#### <140 vs. >=200

```{r}
roc_df %>%
    select(`OGTT 2-hour`, Gender, MutClass, hgba1c) %>%
    filter(`OGTT 2-hour` != "[140,200)") %>%
    mutate(`OGTT 2-hour` = droplevels(`OGTT 2-hour`)) %>%
    tbl_summary(
        by = `OGTT 2-hour`,
        missing_text = "Missing",
        type = list(all_continuous() ~ "continuous2"),
        statistic = list(
            all_continuous() ~
                c("{mean} ({sd})", "{median} ({p25}, {p75})", "{min}, {max}")
        ),
        label = list(
            hgba1c = "HbA1c",
            Hispanicrace = "Hispanic",
            MutClass = "Mutation Class",
            reviewyear = "Year",
            Age_YrEnd = "Age at Year End"
        )
    ) %>%
    add_overall() %>%
    add_p(
        test = list(reviewyear = "fisher.test"),
        test.args = all_tests("fisher.test") ~ list(simulate.p.value = T)
    ) %>%
    separate_p_footnotes() %>%
    as_gt()
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = ngt_agt)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(
    r,
    "all",
    ret = c(
        "threshold",
        "sensitivity",
        "specificity",
        "tpr",
        "tnr",
        "fpr",
        "fnr",
        "npv",
        "ppv"
    )
))) %>%
    fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = agt_cfrd)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(
    r,
    "all",
    ret = c(
        "threshold",
        "sensitivity",
        "specificity",
        "tpr",
        "tnr",
        "fpr",
        "fnr",
        "npv",
        "ppv"
    )
))) %>%
    fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = peds_ngt_agt)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(
    r,
    "all",
    ret = c(
        "threshold",
        "sensitivity",
        "specificity",
        "tpr",
        "tnr",
        "fpr",
        "fnr",
        "npv",
        "ppv"
    )
))) %>%
    fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = peds_agt_cfrd)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(
    r,
    "all",
    ret = c(
        "threshold",
        "sensitivity",
        "specificity",
        "tpr",
        "tnr",
        "fpr",
        "fnr",
        "npv",
        "ppv"
    )
))) %>%
    fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = adult_ngt_agt)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(
    r,
    "all",
    ret = c(
        "threshold",
        "sensitivity",
        "specificity",
        "tpr",
        "tnr",
        "fpr",
        "fnr",
        "npv",
        "ppv"
    )
))) %>%
    fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = adult_agt_cfrd)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(
    r,
    "all",
    ret = c(
        "threshold",
        "sensitivity",
        "specificity",
        "tpr",
        "tnr",
        "fpr",
        "fnr",
        "npv",
        "ppv"
    )
))) %>%
    fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = white_ngt_agt)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(
    r,
    "all",
    ret = c(
        "threshold",
        "sensitivity",
        "specificity",
        "tpr",
        "tnr",
        "fpr",
        "fnr",
        "npv",
        "ppv"
    )
))) %>%
    fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = white_agt_cfrd)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(
    r,
    "all",
    ret = c(
        "threshold",
        "sensitivity",
        "specificity",
        "tpr",
        "tnr",
        "fpr",
        "fnr",
        "npv",
        "ppv"
    )
))) %>%
    fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = black_ngt_agt)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(
    r,
    "all",
    ret = c(
        "threshold",
        "sensitivity",
        "specificity",
        "tpr",
        "tnr",
        "fpr",
        "fnr",
        "npv",
        "ppv"
    )
))) %>%
    fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = black_agt_cfrd)
roc_plot(r)
gt(data.frame(coords(r, "best"))) %>%
    fmt_number(n_sigfig = 3)
gt(data.frame(ci.coords(r, "best", best.policy = "random"))) %>%
    fmt_number(n_sigfig = 3)
gt(data.frame(coords(
    r,
    "all",
    ret = c(
        "threshold",
        "sensitivity",
        "specificity",
        "tpr",
        "tnr",
        "fpr",
        "fnr",
        "npv",
        "ppv"
    )
))) %>%
    fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = more_ngt_agt)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(
    r,
    "all",
    ret = c(
        "threshold",
        "sensitivity",
        "specificity",
        "tpr",
        "tnr",
        "fpr",
        "fnr",
        "npv",
        "ppv"
    )
))) %>%
    fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = more_agt_cfrd)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(
    r,
    "all",
    ret = c(
        "threshold",
        "sensitivity",
        "specificity",
        "tpr",
        "tnr",
        "fpr",
        "fnr",
        "npv",
        "ppv"
    )
))) %>%
    fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = other_ngt_agt)
roc_plot(r)
gt(data.frame(coords(r, "best"))) %>%
    fmt_number(n_sigfig = 3)
gt(data.frame(ci.coords(r, "best", best.policy = "random"))) %>%
    fmt_number(n_sigfig = 3)
gt(data.frame(coords(
    r,
    "all",
    ret = c(
        "threshold",
        "sensitivity",
        "specificity",
        "tpr",
        "tnr",
        "fpr",
        "fnr",
        "npv",
        "ppv"
    )
))) %>%
    fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = other_agt_cfrd)
roc_plot(r)
gt(data.frame(coords(r, "best"))) %>%
    fmt_number(n_sigfig = 3)
gt(data.frame(ci.coords(r, "best", best.policy = "random"))) %>%
    fmt_number(n_sigfig = 3)
gt(data.frame(coords(
    r,
    "all",
    ret = c(
        "threshold",
        "sensitivity",
        "specificity",
        "tpr",
        "tnr",
        "fpr",
        "fnr",
        "npv",
        "ppv"
    )
))) %>%
    fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = hispanic_ngt_agt)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(
    r,
    "all",
    ret = c(
        "threshold",
        "sensitivity",
        "specificity",
        "tpr",
        "tnr",
        "fpr",
        "fnr",
        "npv",
        "ppv"
    )
))) %>%
    fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = hispanic_agt_cfrd)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(
    r,
    "all",
    ret = c(
        "threshold",
        "sensitivity",
        "specificity",
        "tpr",
        "tnr",
        "fpr",
        "fnr",
        "npv",
        "ppv"
    )
))) %>%
    fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = non_hispanic_ngt_agt)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(
    r,
    "all",
    ret = c(
        "threshold",
        "sensitivity",
        "specificity",
        "tpr",
        "tnr",
        "fpr",
        "fnr",
        "npv",
        "ppv"
    )
))) %>%
    fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = non_hispanic_agt_cfrd)
roc_plot(r)
gt(data.frame(coords(r, "best"))) %>%
    fmt_number(n_sigfig = 3)
gt(data.frame(ci.coords(r, "best", best.policy = "random"))) %>%
    fmt_number(n_sigfig = 3)
gt(data.frame(coords(
    r,
    "all",
    ret = c(
        "threshold",
        "sensitivity",
        "specificity",
        "tpr",
        "tnr",
        "fpr",
        "fnr",
        "npv",
        "ppv"
    )
))) %>%
    fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(agt ~ hgba1c, data = roc_df)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(
    r,
    "all",
    ret = c(
        "threshold",
        "sensitivity",
        "specificity",
        "tpr",
        "tnr",
        "fpr",
        "fnr",
        "npv",
        "ppv"
    )
))) %>%
    fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(cfrd ~ hgba1c, data = roc_df)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(
    r,
    "all",
    ret = c(
        "threshold",
        "sensitivity",
        "specificity",
        "tpr",
        "tnr",
        "fpr",
        "fnr",
        "npv",
        "ppv"
    )
))) %>%
    fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(agt ~ hgba1c, data = peds_roc)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(
    r,
    "all",
    ret = c(
        "threshold",
        "sensitivity",
        "specificity",
        "tpr",
        "tnr",
        "fpr",
        "fnr",
        "npv",
        "ppv"
    )
))) %>%
    fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(cfrd ~ hgba1c, data = peds_roc)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(
    r,
    "all",
    ret = c(
        "threshold",
        "sensitivity",
        "specificity",
        "tpr",
        "tnr",
        "fpr",
        "fnr",
        "npv",
        "ppv"
    )
))) %>%
    fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(agt ~ hgba1c, data = adult_roc)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(
    r,
    "all",
    ret = c(
        "threshold",
        "sensitivity",
        "specificity",
        "tpr",
        "tnr",
        "fpr",
        "fnr",
        "npv",
        "ppv"
    )
))) %>%
    fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(cfrd ~ hgba1c, data = adult_roc)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(
    r,
    "all",
    ret = c(
        "threshold",
        "sensitivity",
        "specificity",
        "tpr",
        "tnr",
        "fpr",
        "fnr",
        "npv",
        "ppv"
    )
))) %>%
    fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(agt ~ hgba1c, data = white_roc)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(
    r,
    "all",
    ret = c(
        "threshold",
        "sensitivity",
        "specificity",
        "tpr",
        "tnr",
        "fpr",
        "fnr",
        "npv",
        "ppv"
    )
))) %>%
    fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(cfrd ~ hgba1c, data = white_roc)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(
    r,
    "all",
    ret = c(
        "threshold",
        "sensitivity",
        "specificity",
        "tpr",
        "tnr",
        "fpr",
        "fnr",
        "npv",
        "ppv"
    )
))) %>%
    fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(agt ~ hgba1c, data = black_roc)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(
    r,
    "all",
    ret = c(
        "threshold",
        "sensitivity",
        "specificity",
        "tpr",
        "tnr",
        "fpr",
        "fnr",
        "npv",
        "ppv"
    )
))) %>%
    fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(cfrd ~ hgba1c, data = black_roc)
roc_plot(r)
gt(data.frame(ci.coords(r, "best", best.policy = "random"))) %>%
    fmt_number(n_sigfig = 3)
gt(data.frame(coords(
    r,
    "all",
    ret = c(
        "threshold",
        "sensitivity",
        "specificity",
        "tpr",
        "tnr",
        "fpr",
        "fnr",
        "npv",
        "ppv"
    )
))) %>%
    fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(agt ~ hgba1c, data = more_roc)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(
    r,
    "all",
    ret = c(
        "threshold",
        "sensitivity",
        "specificity",
        "tpr",
        "tnr",
        "fpr",
        "fnr",
        "npv",
        "ppv"
    )
))) %>%
    fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(cfrd ~ hgba1c, data = more_roc)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(
    r,
    "all",
    ret = c(
        "threshold",
        "sensitivity",
        "specificity",
        "tpr",
        "tnr",
        "fpr",
        "fnr",
        "npv",
        "ppv"
    )
))) %>%
    fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(agt ~ hgba1c, data = other_roc)
roc_plot(r)
gt(data.frame(coords(r, "best"))) %>%
    fmt_number(n_sigfig = 3)
gt(data.frame(ci.coords(r, "best", best.policy = "random"))) %>%
    fmt_number(n_sigfig = 3)
gt(data.frame(coords(
    r,
    "all",
    ret = c(
        "threshold",
        "sensitivity",
        "specificity",
        "tpr",
        "tnr",
        "fpr",
        "fnr",
        "npv",
        "ppv"
    )
))) %>%
    fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(cfrd ~ hgba1c, data = other_roc)
roc_plot(r)
gt(data.frame(coords(r, "best"))) %>%
    fmt_number(n_sigfig = 3)
gt(data.frame(ci.coords(r, "best"))) %>%
    fmt_number(n_sigfig = 3)
gt(data.frame(coords(
    r,
    "all",
    ret = c(
        "threshold",
        "sensitivity",
        "specificity",
        "tpr",
        "tnr",
        "fpr",
        "fnr",
        "npv",
        "ppv"
    )
))) %>%
    fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(agt ~ hgba1c, data = hispanic_roc)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(
    r,
    "all",
    ret = c(
        "threshold",
        "sensitivity",
        "specificity",
        "tpr",
        "tnr",
        "fpr",
        "fnr",
        "npv",
        "ppv"
    )
))) %>%
    fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(cfrd ~ hgba1c, hispanic_roc)
roc_plot(r)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(
    r,
    "all",
    ret = c(
        "threshold",
        "sensitivity",
        "specificity",
        "tpr",
        "tnr",
        "fpr",
        "fnr",
        "npv",
        "ppv"
    )
))) %>%
    fmt_number(n_sigfig = 3)
```
